---
output: github_document
bibliography: inst/REFERENCES.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  eval = FALSE
)
```



# Tukey's g-and-h probability distribution


## Presentation

The package provides distribution, density and quantile functions of the Tukey's
g-and-h probability distribution [@tukey1977], as well as functions for random
number generation, parameter estimation and testing.

In the current version of the package, the g-and-h distribution can be fitted
through:

* indirect inference [@bee2019a]
* the quantile estimator [@hoaglin1985]
* maximum likelihood [@bee2019b]

whereas the hypothesis $h=0$ (which makes the g-and-h distribution, a g
distribution) is tested by means of the log-likelihood ratio test procedure
proposed in @bee2021b.



## An example

Fit the g-and-h distribution to dataset `BDSF` on operational losses by means
of indirect inference [@bee2019a], and quantile estimator [@hoaglin1985]:
```{r}
library(tukeyGH)
data("BDSF")

modII <- fitGH(BDSF, method = "iinference")
summary(modII)

modQu <- fitGH(BDSF, method = "quantile")
summary(modQu)
```



## References


